\documentclass[11pt, oneside]{article}
\usepackage[margin=0.5in]{geometry}
\geometry{letterpaper}           
\usepackage[parfill]{parskip}    
\usepackage{graphicx}				
\usepackage{amssymb}
\usepackage{xcolor}
\pagecolor{white}
\usepackage[colorlinks = true, linkcolor = blue, urlcolor  = blue]{hyperref}
\pagestyle{empty}

\title{Yuri Avdijevski}
\author{Yuri Avdijevski}

\begin{document}

\begin{center}
\section*{Yuri Avdijevski}
Mid-level Software Engineer

\href{dtoxvanilla@gmail.com}{dtoxvanilla@gmail.com}
\end{center}

\subsection*{Profile}

As a mid-level web engineer, I possess extensive experience in developing and maintaining complex web applications. I have a solid understanding of web technologies such as HTML, CSS, JavaScript, and have hands-on experience in using front-end frameworks such as React, Angular, or Vue.js.

My expertise also extends to back-end development, including server-side technologies like Node.js and Express. I have a strong grasp of database management systems like MongoDB, data query language and data manipulation language for APIs like Graphql and Apollo and I am comfortable working with RESTful APIs to connect front-end and back-end components..

\medskip
\subsection*{Experience}

\textbf{Lavanda UK Ltd}
\hfill
\textit{March 2022 – Present}

\textbf{Software Engineer}

\begin{itemize}
  \item Developed and implemented an AI-powered API feature, improving system performance and enhancing user experience by automating tasks and enabling data-driven decision-making.
  \item Developed and implemented E2E testing, integration and unit testing, covering the entire flow of the applications using Cypress and Argos.
  \item Contributed to the global scaling of an established startup, impacting application architecture while primarily focusing on product engineering.
  \item Developed various web applications using modern front-end frameworks and server-side technologies, gaining valuable experience in cross-functional collaboration across different parts of the stack including front-end, back-end, and database development.
  \item Continuously acquired knowledge of cutting-edge technologies from their latest patch or version releases, such as React, Angular, Node.js, Graphql, AWS, among others whilst working collaboratively with the team to deliver quality products on time using agile methodologies.
  \item Prioritized tasks effectively and accomplished goals by collaborating with cross-functional teams, contributing to the growth and success of Lavanda.
\end{itemize}

\medskip

\textbf{Restless Beings}
\hfill
\textit{March 2022 – present}

\textbf{Software Engineer}

\begin{itemize} 
  \item My role at Restless Beings is developing and maintaining organizations website, revamping its design, functionalities, utilities and ensuring that the various systems within the charity consistently deliver on the constant changing needs. This is a not-for-profit work I do.
  \item Technology: current Prod product has been built on Nuxt2. Starting March of this year, I have been co-authoring Restless Beings entire website and app overhaul, which includes, but it is not limited to: road-map, architecture, design and implementation.
  \item Some key responsibilities and objectives accomplished:
  \item Designed and developed dynamic and responsive UI components using Nuxt's built-in Vue.js capabilities, ensuring a smooth user experience across different devices and screen sizes. I have introduced Storybook with the component detail layout for a better DX.
  \item Integrated an API client with Nuxt Axios module to communicate with the backend server, enabling seamless data retrieval and submission for various app functionalities, such as donation processing and volunteer management.
  \item Utilized Nuxt Content module to create and manage dynamic content pages, such as news updates and event announcements, enabling the charity organization to easily publish and update information on the app.
  \item Implemented a donation tracking feature using Vuex state management, allowing users to view their donation history, track progress towards fundraising goals, and generate reports for transparency and accountability purposes on the Restless Beings protected Admin Dashboard.

\end{itemize}

\medskip

\subsection*{Education}
\textbf{Kingsland University, USA}
\hfill
\textit{Full Stack Developer – 2021}

Gained expertise in both Front End and Back End technologies, studied methodologies, APIs, architectural design, testing etc.

\end{document}
